Paper Figures and Text

### 2023-02-09 Fish Data Analysis/Paper_Figures.qmd
Fixed code not pulling from correct V2 files
Code was only pulling from the base V2 file as I had a hard coded link in the middle. Now it uses the correct data files each time

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
```

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

>>>>

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB","#FF0000")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#0031B8","#1553BE","#2B76C4","#4098CA","#55BACF","#6BDDD5","#80FFDB","#FF0000")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))
